IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-10-18 paper/extensions.tex
minor fixes
nits

\section{Extensions, Limitations, and Future Direction}
\label{sec:extensions}
\label{sec:extensions:labeled}

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
For example, COWL provides a labeled version of the XHR object.
%while LIO implements a labeled file system, used in server-side web
%applications~\cite{hails}.

Our system can be extended with constructs such as labeled values,
labeled mutable references, clearance, and privileges.
For space reasons, we provide full formal semantics (including the soundness
proof with the extensions) in \appendixextfirst{}.

\subsection{External Effects}
\label{sec:extensions:external}
Our embedding assumes that the target language does not have any
primitives that can induce external effects.
%
As discussed in Section~\ref{sec:real}, imposing this restriction
can be challenging.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in an IFC browser must load resources or
perform XHR to be useful.

>>>>

\section{Extensions and Limitations}
\label{sec:extensions}
\label{sec:extensions:labeled}

While the IFC language presented thus far provides the basic
information flow primitives, actual IFC implementations
may wish to extend the minimal system with more specialized
constructs.
For example, COWL provides a labeled version of the XHR object.
%while LIO implements a labeled file system, used in server-side web
%applications~\cite{hails}.
%
Our system can be extended with constructs such as labeled values,
labeled mutable references, clearance, and privileges.
For space reasons, we provide
details of this, including the soundness
proof with the extensions, in \appendixextfirst{}.
%
Here, we instead discuss a limitation of our formalism: the lack of
external effects.

%\subsection{External Effects}
%\label{sec:extensions:external}
Specifically, our embedding assumes that the target language does not
have any primitives that can induce external effects.
%
As discussed in Section~\ref{sec:real}, imposing this restriction
can be challenging.
%
Yet, external effects are crucial when implementing more complex
real-world applications.
%
For example, code in an IFC browser must load resources or
perform XHR to be useful.
